Should I Airbnb My Property?

### 2017-03-07 abb_Writeup.Rmd
adding sensitivity plots

-- Show differences in global numbers and heat maps
-- Re-do the logistic models with potential revenue

@@

@@

Look at difference if breaking down by host type
-- Show new numbers and heat maps
-- Re-do logistic models, extrapolate but divided by hosts

@@

<!-- <!-- Although it gathers considerable interest in both economic and public policy circles, analyses of Airbnb market and their comparison to more traditional long-term leasing strategies remains relatively unaddressed.  This work attempts to fill this void.  -->

>>>>

-- Show differences in global numbers and heat maps

53.3%
```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx'}

  pot.data.ic <- str.data.ic

  pot.data.ic$occ.qtl <- makeWtdQtl(pot.data.ic$pot.occ.rate, return.type='rank')

  pqtl.hm <- abbHeatMap(pot.data.ic,
                x.field='occ.qtl',
                y.field='rate.qtl',
                pref.field='str.pot.pref',
                svm=F, 
                alpha.count=T,
                add.points=T,
                fill.colors=c(abb.col[1], abb.col[5]))
  pqtl.hm <- pqtl.hm + ylab('Nightly Rate (Qtl)')

  pqtl.hm.svm <- abbHeatMap(pot.data.ic,
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.pot.pref',
                   svm=T, 
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))
  pqtl.hm.svm <- pqtl.hm.svm + ylab('Nightly Rate (Qtl)')

```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preferencexxx', fig.lp='xxxx'}

  ggMultiPlots(pqtl.hm, pqtl.hm.svm, cols=2)

-- Re-do the logistic models with potential revenue

@@

Ext is what is happening, potential is what could happening

@@

Look at difference if breaking down by host type

```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

 # Make Basic comparison table
  pref.table <- abbCreateCompTable(ic.df=str.data.ic,
                                   split.field='host.type')

 # Limit to the extrapolated pref type
  pref.table <- pref.table[pref.table$rev.type == 'Extrapolated', ]

  host.data.ic <- str.data.ic

  ps <- which(str.data.ic$host.type == 'Profit Seeker')
  os <- which(str.data.ic$host.type == 'Opportunistic Sharer')
  mu <- which(str.data.ic$host.type == 'Multi-Platform User')
  un <- which(str.data.ic$host.type == 'Unknown')

  host.data.ic$occ.qtl[ps] <- makeWtdQtl(
      host.data.ic$occ.rate[ps], return.type='rank')
  host.data.ic$rate.qtl[ps] <- makeWtdQtl(
    host.data.ic$med.rate[ps], return.type='rank')

  host.data.ic$occ.qtl[os] <- makeWtdQtl(
      host.data.ic$occ.rate[os], return.type='rank')
  host.data.ic$rate.qtl[os] <- makeWtdQtl(
    host.data.ic$med.rate[os], return.type='rank')

  host.data.ic$occ.qtl[mu] <- makeWtdQtl(
      host.data.ic$occ.rate[mu], return.type='rank')
  host.data.ic$rate.qtl[mu] <- makeWtdQtl(
    host.data.ic$med.rate[mu], return.type='rank')

  host.data.ic$occ.qtl[un] <- makeWtdQtl(
      host.data.ic$occ.rate[un], return.type='rank')
  host.data.ic$rate.qtl[un] <- makeWtdQtl(
    host.data.ic$med.rate[un], return.type='rank')

```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx55'}

  ps.raw.hm.svm <- abbHeatMap(host.data.ic[ps, ],
                   x.field='occ.rate',
                   y.field='med.rate',
                   pref.field='str.ext.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=F,
                   fill.colors=c(abb.col[1], abb.col[5]))
  ps.raw.hm.svm <- ps.raw.hm.svm + ylab('Nightly Rate')

  ps.qtl.hm.svm <- abbHeatMap(host.data.ic[ps, ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.ext.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))
  ps.qtl.hm.svm <- ps.qtl.hm.svm + ylab('Nightly Rate (Qtl)')

```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx44'}

ggMultiPlots(ps.raw.hm.svm, ps.qtl.hm.svm, cols=2)

```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx33'}

  os.raw.hm.svm <- abbHeatMap(host.data.ic[os, ],
                   x.field='occ.rate',
                   y.field='med.rate',
                   pref.field='str.ext.pref',
                   svm=T, 
                   alpha.count=F,
                   add.points=T,
                   quantile=F,
                   fill.colors=c(abb.col[1], abb.col[5]))
  os.raw.hm.svm <- os.raw.hm.svm + ylab('Nightly Rate')

  os.qtl.hm.svm <- abbHeatMap(host.data.ic[os, ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.ext.pref',
                   svm=T, 
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))
  os.qtl.hm.svm <- os.qtl.hm.svm + ylab('Nightly Rate (Qtl)')

```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx22'}

ggMultiPlots(os.raw.hm.svm, os.qtl.hm.svm, cols=2)

```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx11'}

  mu.raw.hm.svm <- abbHeatMap(host.data.ic[mu, ],
                   x.field='occ.rate',
                   y.field='med.rate',
                   pref.field='str.ext.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=F,
                   fill.colors=c(abb.col[1], abb.col[5]))
  mu.raw.hm.svm <- mu.raw.hm.svm + ylab('Nightly Rate')

  mu.qtl.hm.svm <- abbHeatMap(host.data.ic[mu, ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.ext.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))
  mu.qtl.hm.svm <- mu.qtl.hm.svm + ylab('Nightly Rate (Qtl)')

```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx1'}

ggMultiPlots(mu.raw.hm.svm, mu.qtl.hm.svm, cols=2)

```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx2'}

  un.raw.hm.svm <- abbHeatMap(host.data.ic[un, ],
                   x.field='occ.rate',
                   y.field='med.rate',
                   pref.field='str.ext.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=F,
                   fill.colors=c(abb.col[1], abb.col[5]))
  un.raw.hm.svm <- un.raw.hm.svm + ylab('Nightly Rate')

  un.qtl.hm.svm <- abbHeatMap(host.data.ic[un, ],
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.ext.pref',
                   svm=T,
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))
  un.qtl.hm.svm <- un.qtl.hm.svm + ylab('Nightly Rate (Qtl)')

```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx23'}

ggMultiPlots(un.raw.hm.svm, un.qtl.hm.svm, cols=2)

-- Show new numbers and heat maps
-- Re-do logistic models, extrapolate but divided by hosts

@@

vertical SVM lines suggest occ rate is biggest issue.  
<!-- <!-- Although it gathers considerable interest in both economic and public policy circles, analyses of Airbnb market and their comparison to more traditional long-term leasing strategies remains relatively unaddressed.  This work attempts to fill this void.  -->
